%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research/Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Post-Doctoral Fellowship}
    {Dr Osvaldo Novais de Oliveira, University of São Paulo}
    {São Carlos, Brazil}
    {Jun. 2017 -- present}
    {
      \begin{cvitems}
        \item {Synthesis of quantum dots.}
        \item {Sensing and characterization of biosensors.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Visiting Scholar}
    {Dr Boxin Zhao, University of Waterloo}
    {Waterloo, Canada}
    {2012 -- 2013}
    {
      \begin{cvitems}
        \item {Synthesis of acrylic pressure sensitive adhesives.}
        \item {Surface modification of polydimethylsiloxane (PDMS).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Researcher}
  {Opalux Inc.}
  {Toronto, Canada}
  {Feb. -- Jul. 2009}
  {
    \begin{cvitems}
      \item {Supported the development of P-INK device (Electrically Active Colour-Based Battery Tester).}
      \item {Helped with technical problems with other product lines.}
      \item {Synthesized nanoparticles on demand.}
      \item {Developed and constructed an electronic voltage tuner (potentiometer) for P-INK device.}
      \item {Responsible for the design, construction and maintenance of company website.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Data Analyst}
    {Ministry of Environment}
    {Toronto, Canada}
    {Sep. -- Dec. 2008}
    {
      \begin{cvitems}
        \item {Analyzed past data for outliers for the drinking water survey program (DWSP).}
        \item {Corrected outliers when possible with actual raw data.}
        \item {Compiled past data into the appropriate reports.}
        \item {Supported the DWSP questionnaire (\textit{i.e.} contacted and requested information from all participating drinking water works.)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher}
    {Dr Andrew McWilliams, Ryerson University}
    {Toronto, Canada}
    {May -- Aug. 2008}
    {
      \begin{cvitems}
        \item {Supported the development of polymer precursors.}
        \item {Synthesized several analog precursors.}
        \item {Utilized the computational chemistry program HyperChem in the construction of precursors.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
